formula1

### 2025-03-03 inst/formula1.Rmd
remove old-style flawed code

Now we can test the hypothesis that Hamilton's wet strength `S` is zero:

```{r,testwetstrengthzero,cache=TRUE}
pnames(H)
H9 <- keep_flawed(H,c("S",pnames(H)[1:8]))
specificp.gt.test(H9,"S",0)
```

now profile likelihood:

```{r,doproflikn,cache=TRUE}
H9
maxp(H9)
p <- seq(from=0.11,to=0.13,len=50)
u01 <- profsupp(H9,"Hamilton",p,n=01)
plot(p,u01)
u20 <- profsupp(H9,"Hamilton",p,n=20)
plot(p,u20)
u50 <- profsupp(H9,"Hamilton",p,n=50)
plot(p,u50)
uu <- pmax(u01,u20,u50)
plot(p,uu)
```

>>>>

Now in principle we can test the hypothesis that Hamilton's wet
strength `S` is zero but I have not done this yet.
